\chapter{Alternatives}
Even though I mentioned that there are several alternatives to \emph{Vulkan}, I propose an overlook of some development
kits that are widely used by the industry on different systems.

\section{Metal}
It is an \gls{api} that provides a high performance access to the \gls{gpu}. Allows a low level access to the hardware,
which maximizes the graphical quality and the computation power for applications runnng under \emph{iOS}, \emph{macOS}
and \emph{tvOS}. \emph{Metal} owns a simplified \gls{api}, precompiled shaders and multithread support. It is focused
for developers that want push to the limit the integrated graphic cards in \emph{Apple} mobile devices.

Released on 2015 as an alternative to \emph{OpenGL}. Seeks a more direct access to the hardware of the devices - the
same objective as \emph{Vulkan}. Being closer to the \emph{metal} of the machine the resource consumption and access
is reduced. Some of the new features includes a better synchronization between the \gls{gpu} and the \gls{cpu} for
reducing the amount of data the \gls{cpu} has to provide to the \gls{gpu}: the logic behind is that the each time the
graphic card needs to draw a scene, the \gls{cpu} has to send the commands explicitly. By means of the resource
sharing, the graphic card can access to the data with no need of intermediary.

\section{OpenGL}
Standard specification that defines a multilanguage and multiplatfrom \gls{api}. The initial release was performed
in 1992. Introduced as a solution to the graphical problems existing at early 80s: companies had to outsource
programmers for writing specific drivers for each kind of hardware. Many times these kind of solutions were not the
most optimal, without considering the financial implications.

During mid-90s, the multimedia industry tried to unify two most relevant technologies: \emph{Microsoft}'s
\emph{Direct3D} and \emph{OpenGL}. The objective was to create an industry graphical libraries standard. Because of a
lack of funding and supporting the project failed two years after the proposal.

\emph{OpenGL} is available to anyone, but it is not Open Source since the source code is not available. This
\gls{api} is an open specification that describes the interface the programmer uses and expected behavior. The
implementation that is Open Source is called \emph{Mesa3D}. It is a good start point for the programmers that want to
introduce themselves to the graphical libraries world. Nowadays \emph{OpenGL} does not have a huge relevance in
desktop environments, a few companies uses this standard as a first option for developing. This specification is very
used for the creation of graphical engines, simulators and mobile devices applications.

\section{DirectX}
Made up by a collection of \gls{api}s developed for ease the task related with multimedia, videos and - above all -
videogames. Consists of different libraries for drawing in 2D, 3D, input device processing, network communications,
audio playing and recording...

It is only available in Microsoft's platforms, such as \emph{Windows} or \emph{Xbox}. However, it is being developed an
Open Source implementation for \emph{Unix} systems - this project is called \emph{WineHQ}.

The initial release was at ending 1995s. In the past, games were executed directly under \emph{DOS} system, where no
specific \gls{api} was employed for multimedia development. During those years, the market demand of multimedia
applications was going greater and greater, and there is no native solutions. The first version of \emph{DirectX} - also
called \emph{Direct3D} - was integrated into \emph{Windows 95}, as a substitute of \gls{dci} and \emph{WinG Windows 3.1}
\gls{api}.

\emph{Direct3D} is focused in game development. During many years the \gls{api} implementation has been increased, and
many optimizations have been included. When the \emph{Xbox} consoles were put on sale a specific \gls{api} was created
for the consoles - same happened with the mobile system\emph{ Windows Phone}. \emph{Microsoft} still supports to
\emph{OpenGL} inside their desktop systems. This is because applications like \gls{cad} and simulators consumes that
\gls{api}. For taking advantage of \emph{OpenGL} features, \emph{Microsoft} has created a half-support between
\emph{DirectX} and \emph{OpenGL}. They offer to developers different choices upon implementing their solutions.
